---
title: "Comparison of cars with automatic and manual gearboxes"
author: "Pavel Naumov"
date: "05/12/2019"
output:
  html_document: default
  word_document: default
  pdf_document: 
    fig_crop: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First glance at the Motor Trend dataset 

First of all we are going to make first glance at our data set.
This is the "Motor Trend Car Road Tests" dataset.The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r cars}
car<-datasets::mtcars
head(car, 10)
```


## Multivarible regression 
As the first step we try to include all variables to our model and estimate their roles:

```{r Multivariable, echo=TRUE} 
summary(lm(mpg ~ ., data = car))$coefficients
```
As we can see a lot of variables have parameter P>0.05.
As the next step we try to exclude bad variables step by step (see appendix).

As a results of backward-elimination process we have a table with only 3 columns:  
wt - Weight (1000 lbs);
qsec - 1/4 mile time;
am - Transmission (0 = automatic, 1 = manual).

```{r new table, echo=TRUE}
car2<-subset(car, select = c(mpg, wt, qsec,am))
summary(lm(mpg ~ .-1, data = car2))$coefficients
```


## Conclusion   
Base on the final model we can estimate the influence of mechanic gearbox to miles per gallon with 95% confidence.
```{r  conclusion, echo=TRUE}
fit<-summary(lm(mpg ~ . -1, data = car2))$coefficients

mechanic_gearbox<- fit[3,1]+c(-1, 1) * qt(0.975, df = (lm(mpg ~ . -1, data = car2))$df) * fit[3, 2]
print(mechanic_gearbox)

par(mfrow = c(2,2))
plot(lm(mpg ~ . -1, data = car2))

```

Mechanic gearbox increase mpg from 2.2 up to 6.4 miles per gallon with 95% confidence.

\newpage

## Appendix

And we can automate this backward-elimination process:
```{r Backward-elimination, echo=TRUE}
car2<-car
variable_name <- names(sort(summary(lm(mpg ~ ., data = car2))$coefficients[,"Pr(>|t|)"], decreasing = TRUE)[1])
variable_P<-sort(summary(lm(mpg ~ ., data = car2))$coefficients[,"Pr(>|t|)"], decreasing = TRUE)[1]
print(variable_P)


while (variable_P>0.05 && variable_name!="(Intercept)") {
car2<-car2[, -which(names(car2)==variable_name)]
print(variable_P)
variable_name<-names(sort(summary(lm(mpg ~ ., data = car2))$coefficients[,"Pr(>|t|)"], decreasing = TRUE)[1])

variable_P<-sort(summary(lm(mpg ~ ., data = car2))$coefficients[,"Pr(>|t|)"], decreasing = TRUE)[1]
}

```

Finally in our table we have only 3 columns 
wt - Weight (1000 lbs) 
qsec - 1/4 mile time
am - Transmission (0 = automatic, 1 = manual)

```{r  after Backward-elimination, echo=TRUE}
summary(lm(mpg ~ . -1, data = car2))$coefficients
```
